---
title: "Homework 5"
author: "Zoey Zhao"
date: "11/19/2021"
output: github_document
---

```{r message=FALSE}
library(tidyverse)
```

## Problem 1

For this problem, we are interested in the data released by _The Washington Post_ in homicides in 50 large U.S. cities. The code chunk below imports and cleans the data.

```{r message=FALSE}
homicide_data <- read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv", na = c("", "Unknown"))%>%
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "Unsolved",
      disposition == "Open/No arrest" ~ "Unsolved",
      disposition == "Closed by arrest" ~ "Solved"
    ))%>%
  relocate(city_state)%>%
  filter(city_state != "TulsaAL")
```

Let's focus on Baltimore, MD.

```{r}
baltimore_df <-
  homicide_data%>%
  filter(city_state == "BaltimoreMD")

baltimore_summary <-
  baltimore_df%>%
  summarize(
    unsolved = sum(resolution == "Unsolved"),
    n = n())

baltimore_test <-
  prop.test(
  x = baltimore_summary%>%pull(unsolved),
  n = baltimore_summary%>%pull(n)
)

baltimore_test%>%
  broom::tidy()
```

There are 64.6% of homicides in Baltimore are not solved, with a 95% CI 62.8%-66.3%.

Let's try to iterate across the cities.
1. Write a function
```{r}
prop_test_function <- function(city_df) {
  city_summary <-
  city_df%>%
  summarize(
    unsolved = sum(resolution == "Unsolved"),
    n = n()
    )
  city_test <-
  prop.test(
  x = city_summary%>%pull(unsolved),
  n = city_summary%>%pull(n)
  )
  
  return(city_test)
}
```

2. Iterate across all cities
```{r}
nested_df <-
  homicide_data%>%
  nest(data = uid:resolution)%>%
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  )%>%
  select(city_state, tidy_results)%>%
  unnest(tidy_results)%>%
  select(city_state, estimate, starts_with("conf"))

nested_df
```

Create a plot that shows the estimates and CIs for each city, and organize cities according to the proportion of unsolved homicides.

```{r}
nested_df%>%
  mutate(city_state = fct_reorder(city_state, estimate))%>%
  ggplot(aes(x = city_state, y = estimate))+
  geom_point()+
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))+
  labs(title = "Proportion of Unsolved Homicides with CIs",
       x = "Cities", 
       y = "Proportion of unsolved homicides")

```
















