---
title: "Homework 5"
author: "Zoey Zhao"
date: "11/19/2021"
output: github_document
---

```{r message=FALSE}
library(tidyverse)
```

## Problem 1

For this problem, we are interested in the data released by _The Washington Post_ in homicides in 50 large U.S. cities. The code chunk below imports and cleans the data.

```{r message=FALSE}
homicide_data <- read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv", na = c("", "Unknown"))%>%
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "Unsolved",
      disposition == "Open/No arrest" ~ "Unsolved",
      disposition == "Closed by arrest" ~ "Solved"
    ))%>%
  relocate(city_state)%>%
  filter(city_state != "TulsaAL")
```

Let's focus on Baltimore, MD.

```{r}
baltimore_df <-
  homicide_data%>%
  filter(city_state == "BaltimoreMD")

baltimore_summary <-
  baltimore_df%>%
  summarize(
    unsolved = sum(resolution == "Unsolved"),
    n = n())

baltimore_test <-
  prop.test(
  x = baltimore_summary%>%pull(unsolved),
  n = baltimore_summary%>%pull(n)
)

baltimore_test%>%
  broom::tidy()
```

There are 64.6% of homicides in Baltimore are not solved, with a 95% CI 62.8%-66.3%.

Let's try to iterate across the cities.
1. Write a function
```{r}
prop_test_function <- function(city_df) {
  city_summary <-
  city_df%>%
  summarize(
    unsolved = sum(resolution == "Unsolved"),
    n = n()
    )
  city_test <-
  prop.test(
  x = city_summary%>%pull(unsolved),
  n = city_summary%>%pull(n)
  )
  
  return(city_test)
}
```

2. Iterate across all cities
```{r}
nested_df <-
  homicide_data%>%
  nest(data = uid:resolution)%>%
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  )%>%
  select(city_state, tidy_results)%>%
  unnest(tidy_results)%>%
  select(city_state, estimate, starts_with("conf"))

nested_df
```

Create a plot that shows the estimates and CIs for each city, and organize cities according to the proportion of unsolved homicides.

```{r}
nested_df%>%
  mutate(city_state = fct_reorder(city_state, estimate))%>%
  ggplot(aes(x = city_state, y = estimate))+
  geom_point()+
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))+
  labs(title = "Proportion of Unsolved Homicides with CIs",
       x = "Cities", 
       y = "Proportion of unsolved homicides")

```

## Problem 2

Start with a dataframe containing all file names.
```{r}
file_name <-
  tibble(list.files("./data/zip_data/"))%>%
           mutate(name = list.files("./data/zip_data/"))%>%
           select(name)
    
```

Iterate over file names and read in data for each subject and saving the result as a new variable in the dataframe.

```{r message=FALSE}
all_file <-
  data_frame(name = pull(file_name, name)) %>%
  mutate(data = map(name,      
           ~ read_csv(file.path("./data/zip_data", .))
           )
         )

unnest(all_file)
```

Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary

```{r}
tidy_data<-
  all_file%>%
  unnest()%>%
  separate(name, c("arm", "other"), sep = "_")%>%
  mutate(subject_id = c(1:20),
         arm = as.factor(case_when(arm == "con" ~ "Control",
                         arm == "exp" ~ "Experimental")))%>%
  relocate(subject_id)%>%
  select(!other)%>%
  pivot_longer(week_1:week_8, names_to = "week", names_prefix = "week_")

tidy_data
```

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}
tidy_data%>%
  ggplot(aes(x = week , y = value, color = arm))+
  geom_point()+
  geom_line(aes(group = subject_id))+
  labs(title = "Spaghetti Plot of Observations over Time of 20 subjects",
       y = "Observation",
       x = "Time (week)")
```

Subjects in experimental group seems to have overall higher levels of observations than subjects in control group during the 8-week period of time. The level of observation in experimental group has a trend of growing over time, and the level of observation in control group does not have any obvious changes overall in 8 weeks.

## Problem 3














